Replication of Gantman et al. 2024

### 2024-04-10 manuscript.qmd
automate the eeg quality exclusion

@@

exclude_for_eeg_quality_study_1 <- c("34")
```

@@

eeg_data_study_1 <- read_csv("data/phase_1/final/eeg.csv", col_types = "cdcllcdc") %>%
  filter(!subject %in% excluded_subjects_study_1)
```

@@

exclude_for_eeg_quality <- c()
```

@@

mean_good_trials <- mean(count_good_trials$n)
sd_good_trials <- sd(count_good_trials$n)

>>>>

eeg_data_study_1 <- read_csv("data/phase_1/final/eeg.csv", col_types = "cdcllcdc")
```

@@

exclude_for_eeg_quality_study_1 <- count_good_trials_study_1 %>%
  filter(percent < 75) %>% 
  pull(subject)
```

@@

@@

exclude_for_eeg_quality <- count_good_trials %>%
  filter(percent < 75) %>%
  pull(subject)
```

@@
